### 2014-11-20 Papers/ms.tex
Paper

% Set values so you can have a title
\title{}
\author{Brendon J. Brewer}
\date{\today}

% Document starts here
\begin{document}

@@

\abstract{This is the abstract}

\section{Introduction}
Blah blah

>>>>

% Set values so you can have a title
\title{}
\title{Flexible trans-dimensional modelling of gravitational lenses}
\author{Brendon J. Brewer and David Huijser}
\date{Department of Statistics, The University of Auckland\\
Private Bag 92019, Auckland 1142, New Zealand\\
\vspace{0.3cm}
{\tt bj.brewer@auckland.ac.nz}}
% Document starts here
\begin{document}

@@

\abstract{Gravitational lensing is a powerful astrophysical tool for measuring
masses}

\section{Introduction}

\section{Source and Lens Models}

\section{The Cosmic Horseshoe}

\section{Other Systems}
